Of judges, aliens and total preorders

### 2021-03-06 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: split up a slide with a lot of text
feat: not sure
feat: notes

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{stmaryrd}

@@

% Notes
% Talk using pympress: brew install pympress
% Talk command: pympress -t 40 -n right ~/Documents/master/1901/presentation/1901_3230880_philip_heltweg_presentation.pdf
\setbeameroption{show notes on second screen=right} % Both
% Coloring note-pages
\setbeamertemplate{note page}{\pagecolor{yellow!15}\insertnote\vfill\insertframenumber}
\setbeamertemplate{note page}{
	\pagecolor{yellow!15}
	\medskip
	SLIDE: \insertframenumber\\
	TITLE: \insertframetitle,

@@

\frame{\titlepage}

@@

\begin{frame}{Courtroom example: Revision}

@@

    \begin{itemize}
        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
        \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
              \begin{itemize}
                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
                  \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
              \end{itemize}
    \end{itemize}

@@

\begin{frame}{Properties of BM Revision Operators}
    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
        \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
        \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
        \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
        \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
        \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
    \end{enumerate}

    \note{
        \begin{itemize}
            \item properties
        \end{itemize}
    }
\end{frame}

@@

@@

\begin{frame}{A concrete operator: Setup}
    \begin{itemize}
        \item Function p mapping worlds to real numbers: $p: W^{\pm} \mapsto \mathds{R}$
        \item Interval representing a world: $(p(x^{+}), p(x^{-}))$
        \item Distance between representations: $p(x^{-}) - p(x^{+}) = a > 0$
        \item Define a tpo from $p$: $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
    \end{itemize}

>>>>

\documentclass[12pt, notheorems]{beamer}
%\documentclass[12pt, notheorems, handout]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{stmaryrd}

@@

% Unique numbering scheme for definitions and theorems with the "notheorems" options on loading beamer
% see https://tex.stackexchange.com/questions/82415/beamer-different-numbering-for-theorems-examples-definition-and-lemma
\makeatletter
    \ifbeamer@countsect
      \newtheorem{theorem}{\translate{Theorem}}[section]
    \else
      \newtheorem{theorem}{\translate{Theorem}}
    \fi
    \newtheorem{corollary}{\translate{Corollary}}
    \newtheorem{fact}{\translate{Fact}}
    \newtheorem{lemma}{\translate{Lemma}}
    \newtheorem{problem}{\translate{Problem}}
    \newtheorem{solution}{\translate{Solution}}

    \theoremstyle{definition}
    \newtheorem{definition}{\translate{Definition}}
    \newtheorem{definitions}{\translate{Definitions}}

    \theoremstyle{example}
    \newtheorem{example}{\translate{Example}}
    \newtheorem{examples}{\translate{Examples}}

    % Compatibility
    \newtheorem{Beispiel}{Beispiel}
    \newtheorem{Beispiele}{Beispiele}
    \theoremstyle{plain}
    \newtheorem{Loesung}{L\"osung}
    \newtheorem{Satz}{Satz}
    \newtheorem{Folgerung}{Folgerung}
    \newtheorem{Fakt}{Fakt}
    \newenvironment{Beweis}{\begin{proof}[Beweis.]}{\end{proof}}
    \newenvironment{Lemma}{\begin{lemma}}{\end{lemma}}
    \newenvironment{Proof}{\begin{proof}}{\end{proof}}
    \newenvironment{Theorem}{\begin{theorem}}{\end{theorem}}
    \newenvironment{Problem}{\begin{problem}}{\end{problem}}
    \newenvironment{Corollary}{\begin{corollary}}{\end{corollary}}
    \newenvironment{Example}{\begin{example}}{\end{example}}
    \newenvironment{Examples}{\begin{examples}}{\end{examples}}
    \newenvironment{Definition}{\begin{definition}}{\end{definition}}
\makeatother

% Notes
% Talk using pympress: brew install pympress
% Talk command: pympress -t 40 -n right ~/Documents/master/master-seminar/presentation/1901_3230880_philip_heltweg_presentation.pdf
\setbeameroption{show notes on second screen=right} % Both

% Coloring note-pages
\setbeamertemplate{note page}{\pagecolor{yellow!15}\insertnote\vfill\insertframenumber}
\setbeamertemplate{note page}{
	\pagecolor{yellow!15}
	\medskip
	SLIDE: \insertframenumber\\
	TITLE: \insertframetitle,

@@

\frame{\titlepage}
\note{
    \begin{itemize}
        \item Folien sind nummeriert unten rechts, bei Fragen am besten Nummer aufschreiben
    \end{itemize}
}

@@

\begin{frame}{Courtroom example: Revision 1}

@@

    \begin{itemize}
        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
    \end{itemize}

@@

\begin{frame}{Courtroom example: Revision 2}
    \begin{itemize}
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
        \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
              \begin{itemize}
                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
                  \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
              \end{itemize}
    \end{itemize}

\begin{frame}{Properties of BM Revision Operators: Basic properties}
    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
        \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
        \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
    \end{enumerate}

    \note{
        \begin{itemize}
            \item \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$. In addition, the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
        \end{itemize}
    }
\end{frame}

\begin{frame}{Properties of BM Revision Operators: Common rules in iterated belief change}
    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
        \setcounter{enumi}{2}
        \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
    \end{enumerate}

    \note{
        \begin{itemize}
            \item The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change. Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}. This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996}, which minimises change in conditional beliefs.
            \item If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}). These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2}, by Darwiche and Pearl \cite{Darwiche1997}, discussed in section \ref{chapter:dp-agm-postulates}.
            \item In a similar way, \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}. It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$, if $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$. This property was not only proposed by Booth and Meyer \cite{Booth2006a}, but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
            \item These properties define tpo-revision with one input sentence. Booth and Meyer relate them to the AGM postulates for belief set revision \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
        \end{itemize}
    }
\end{frame}

\begin{frame}{Properties of BM Revision Operators: Supplementary rationality properties }
    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
        \setcounter{enumi}{5}
        \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
        \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
    \end{enumerate}

    \note{
        \begin{itemize}
            \item With \ref{AST6} and \ref{AST7}, Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent. These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}. \ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for revision by any possible evidence $\gamma$, $y$ must still be at least as plausible as $x$. \ref{AST7} is the equivalent property for strict preference.
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}[fragile]{Non-priotized revision}
    \begin{figure}[H]
        \centering
        \begin{tikzpicture}[scale=1]
            \begin{axis}[
                    xticklabels={},
                    yticklabels={},
                    extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                    extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                    ytick style={draw=none},
                    xtick style={draw=none},
                    axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                            empty={mark=*, fill=white},
                            filled={mark=*, fill=black}
                        },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 7 empty
                        3 7 filled

                        2 5 empty
                        4 5 filled

                        6 2 filled
                        8 2 empty

                        6 1 filled
                        8 1 empty
                    };
            \end{axis}
        \end{tikzpicture}
        \caption{Non-prioritised revision by $\alpha = r$}
        \label{fig:example-non-prio-revision}
    \end{figure}

    \note{
        \begin{itemize}
            \item Es gibt postulate die erfordern, dass neuen Informationen immer geglaubt wird und sie in das belief set aufgenommen werden, e.g. \ref{E2} als $\alpha \in B(\mathbb{E}\ast\alpha)$
            \item BM revision operatoren sind "non priotized revision", d.h. neue informationen müssen nicht teil des belief sets werden wie hier gezeigt
            \item aber auch erinnerung: admissible revision von BM erfordert (\ref{AST3} - \ref{AST5}), dass neue informationen nicht ignoriert werden, hier r verändert die conditional beliefs
            \item das im gegensatz zu natural revision by boutilier welches minimal change für conditional beliefs fordert
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{A concrete operator \footnote{as shown in \cite{Booth2011}}: Setup}
    \begin{itemize}
        \item Function p mapping worlds to real numbers: $p: W^{\pm} \mapsto \mathds{R}$
        \item Interval representing a world: $(p(x^{+}), p(x^{-}))$
        \item Distance between representations: $p(x^{-}) - p(x^{+}) = a > 0$
        \item Define a tpo from $p$: $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
    \end{itemize}
